Manuscript

### 2015-01-27 inst/simulation/manuscript.Rmd
...

plotCIProportions <- function(credibilityIntervals) {
  p <- ggplot(credibilityIntervals, aes(scenario, Proportion, shape=Interval, colour=modelName)) +
    geom_hline(aes(yintercept=.5), color="grey90") +
    geom_hline(aes(yintercept=.95), color="grey90") +
    geom_point() +
    scale_shape_manual(values=c(16, 1)) + scale_colour_manual("Model", values=c("darkgray", "black"), labels=c("T", "ST")) +
    theme_minimal(base_size=10) + theme(panel.border=element_rect(fill="transparent")) +
    xlab("Scenario") + ylab("Proportion within CI") +
    facet_wrap(~panel) + ylim(0, 1) +
    theme(panel.grid.major=element_blank(), panel.grid.minor=element_blank())
  return(p)
}
```

@@

```{r, eval=FALSE}
study <- getStudy(scenario="A") # Get study object, scenario doesn't matter
validation <- Validation(study=study, populationSizeOverEstimate=populationSizeOverEstimate)
populationSizes <- validation$getValidationTemporalPopulationSizes(modelNames=modelNames)
validation$summarizePopulationSize(populationSizes)

meanPopulationSizes <- ddply(populationSizes, .(scenario, modelName), function(x) {
  data.frame(True=mean(x$Observed), Estimated=mean(x$Estimated), Scenario=x$scenario)
})
logPopulationSizes <- populationSizes
logPopulationSizes$Observed <- logPopulationSizes$Observed + 1
logPopulationSizes$Estimated <- logPopulationSizes$Estimated + 1
logMeanPopulationSizes <- ddply(populationSizes, .(scenario, modelName), function(x) {
  data.frame(True=10^mean(log10(x$Observed+1)), Estimated=10^mean(log10(x$Estimated+1)), Scenario=x$scenario)
})
#logPopulationSizes$Observed <- log10(logPopulationSizes$Observed + 1)
#logPopulationSizes$Estimated <- log10(logPopulationSizes$Estimated + 1)
#logMeanPopulationSizes <- ddply(populationSizes, .(scenario, modelName), function(x) {
#  data.frame(True=mean(log10(x$Observed+1)), Estimated=mean(log10(x$Estimated+1)), Scenario=x$scenario)
#})
```

```{r figure-3a, eval=FALSE}
p <- ggplot(populationSizes, aes(Observed, Estimated, colour=modelName)) + geom_point(size=1) +
  stat_smooth(method="lm", aes(colour=modelName), se=F) +
  scale_colour_manual("Model", values=c("lightgray", "darkgray","black"), labels=c("I", "T", "ST")) +
  geom_abline(colour="darkgrey", linetype="longdash") +
  geom_point(data=meanPopulationSizes, aes(True, Estimated, colour=modelName), size=2, shape=15) +
  facet_wrap(~Scenario, scales="free") +
  xlab("True population size") + ylab("Estimated population size") +
  theme_minimal(base_size=10) + theme(panel.border=element_rect(fill="transparent"))
print(p)
saveFigure(p, "manuscript-figure-3a.png", width=8, height=4)
```

```{r figure-3-init-2000}
study <- getStudy(scenario="A") # Get study object, scenario doesn't matter
validation <- Validation(study=study, populationSizeOverEstimate=populationSizeOverEstimate)
populationSizes2000 <- validation$getValidationTemporalPopulationSizes(scenarios=paste0(scenarios, "combined"), modelNames=modelNames)
validation$summarizePopulationSize(populationSizes2000)

meanPopulationSizes2000 <- ddply(populationSizes2000, .(scenario, modelName), function(x) {
  data.frame(True=mean(x$Observed), Estimated=mean(x$Estimated), Scenario=x$scenario)
})
logPopulationSizes2000 <- populationSizes2000
logPopulationSizes2000$Observed <- (logPopulationSizes2000$Observed + 1)
logPopulationSizes2000$Estimated <- (logPopulationSizes2000$Estimated + 1)
logMeanPopulationSizes2000 <- ddply(populationSizes2000, .(scenario, modelName), function(x) {
  data.frame(True=10^mean(log10(x$Observed+1)), Estimated=10^mean(log10(x$Estimated+1)), Scenario=x$scenario)
})
```

```{r figure-3c, eval=FALSE}
p <- ggplot(populationSizes2000, aes(Observed, Estimated, colour=modelName)) + geom_point(size=1) +
  stat_smooth(method="lm", aes(colour=modelName), se=F) +
  scale_colour_manual("Model", values=c("lightgray", "darkgray","black"), labels=c("I", "T", "ST")) +
  geom_abline(colour="darkgrey", linetype="longdash") +
  geom_point(data=meanPopulationSizes2000, aes(True, Estimated, colour=modelName), size=2, shape=15) +
  facet_wrap(~Scenario, scales="free") +
  xlab("True population size") + ylab("Estimated population size") +
  theme_minimal(base_size=10) + theme(panel.border=element_rect(fill="transparent"))
print(p)
saveFigure(p, "manuscript-figure-3c.png", width=8, height=4)
```

```{r figure-3-init-10days, eval=FALSE}
study <- getStudy(scenario="A") # Get study object, scenario doesn't matter
validation <- Validation(study=study, populationSizeOverEstimate=populationSizeOverEstimate)
populationSizes10days <- validation$getValidationTemporalPopulationSizes(scenarios=paste0(scenarios, "10days"), modelNames=modelNames)
validation$summarizePopulationSize(populationSizes10days)

meanPopulationSizes10days <- ddply(populationSizes10days, .(scenario, modelName), function(x) {
  data.frame(True=mean(x$Observed), Estimated=mean(x$Estimated), Scenario=x$scenario)
})
logPopulationSizes10days <- populationSizes10days
logPopulationSizes10days$Observed <- (logPopulationSizes10days$Observed + 1)
logPopulationSizes10days$Estimated <- (logPopulationSizes10days$Estimated + 1)
logMeanPopulationSizes10days <- ddply(populationSizes10days, .(scenario, modelName), function(x) {
  data.frame(True=10^mean(log10(x$Observed+1)), Estimated=10^mean(log10(x$Estimated+1)), Scenario=x$scenario)
})
```

```{r figure-3d, eval=FALSE}
p <- ggplot(populationSizes10days, aes(Observed, Estimated, colour=modelName)) + geom_point(size=1) +
  stat_smooth(method="lm", aes(colour=modelName), se=F) +
  scale_colour_manual("Model", values=c("lightgray", "darkgray","black"), labels=c("I", "T", "ST")) +
  geom_abline(colour="darkgrey", linetype="longdash") +
  geom_point(data=meanPopulationSizes10days, aes(True, Estimated, colour=modelName), size=2, shape=15) +
  facet_wrap(~Scenario, scales="free") +
  xlab("True population size") + ylab("Estimated population size") +
  theme_minimal(base_size=10) + theme(panel.border=element_rect(fill="transparent"))
print(p)
saveFigure(p, "manuscript-figure-3d.png", width=8, height=4)
```

```{r figure-4-test, eval=FALSE}
study <- getStudy(scenario="A")
validation <- Validation(study=study, populationSizeOverEstimate=populationSizeOverEstimate)
x <- validation$validateSpatialPopulationSize(modelNames[1])
```

```{r figure-4a}
study <- getStudy(scenario="A")
validation <- Validation(study=study, populationSizeOverEstimate=populationSizeOverEstimate)
populationCorrelations <- validation$getValidationSpatialPopulationSizes(modelNames=modelNames[1])
populationCorrelations$Scenario <- prettyScenario(populationCorrelations$Scenario)

p <- ggplot(populationCorrelations, aes(True, Correlation)) + geom_point(size=1, colour="black") +
  facet_wrap(~Scenario, ncol=2) + xlab("True population size") +
  theme_minimal(base_size=10) + theme(panel.border=element_rect(fill="transparent"))#, axis.text.x=element_text(angle=45, hjust=.5, vjust=1))
print(p)
saveFigure(p, "manuscript-figure-4a.png", width=4, height=4)
```

```{r figure-4b}
study <- getStudy(scenario="A")
validation <- Validation(study=study, populationSizeOverEstimate=populationSizeOverEstimate)
populationCorrelations <- validation$getValidationSpatialPopulationSizes(scenarios=paste0(scenarios, "combined"), modelNames=modelNames[1])
populationCorrelations$Scenario <- prettyScenario(populationCorrelations$Scenario)

p <- ggplot(populationCorrelations, aes(True, Correlation)) + geom_point(size=1, colour="black") +
  facet_wrap(~Scenario, ncol=2) + xlab("True population size") +
  theme_minimal(base_size=10) + theme(panel.border=element_rect(fill="transparent"))#, axis.text.x=element_text(angle=45, hjust=.5, vjust=1))
print(p)
saveFigure(p, "manuscript-figure-4b.png", width=4, height=4)
```

```{r figure-4c}
study <- getStudy(scenario="A")
validation <- Validation(study=study, populationSizeOverEstimate=populationSizeOverEstimate)
populationCorrelations <- validation$getValidationSpatialPopulationSizes(scenarios=paste0(scenarios, "10days"), modelNames=modelNames[1])
populationCorrelations$Scenario <- prettyScenario(populationCorrelations$Scenario)

p <- ggplot(populationCorrelations, aes(True, Correlation)) + geom_point(size=1, colour="black") +
  facet_wrap(~Scenario, ncol=2) + xlab("True population size") +
  theme_minimal(base_size=10) + theme(panel.border=element_rect(fill="transparent"))#, axis.text.x=element_text(angle=45, hjust=.5, vjust=1))
print(p)
saveFigure(p, "manuscript-figure-4c.png", width=4, height=4)
```

```{r figure-5a}
study <- getStudy(scenario="A")
validation <- Validation(study=study, populationSizeOverEstimate=populationSizeOverEstimate)
a <- validation$getValidatedCredibilityIntervalsProportions(modelNames=modelNames)
b <- validation$getValidatedCredibilityIntervalsProportions(modelNames=modelNames, probs=c(.25, .75), probsName="50%")
credibilityIntervals <- rbind(a, b)

p <- ggplot(credibilityIntervals, aes(scenario, Proportion, shape=Interval, colour=modelName)) + geom_point() +
  scale_shape_manual(values=c(16, 1)) + scale_colour_manual("Model", values=c("darkgray", "black"), labels=c("T", "ST")) +
  theme_minimal(base_size=10) + theme(panel.border=element_rect(fill="transparent")) +
  xlab("Scenario") + ylab("Proportion within CI")
print(p)
saveFigure(p, "manuscript-figure-5a.png", width=4, height=2)
```

```{r figure-5b}
study <- getStudy(scenario="A")
validation <- Validation(study=study, populationSizeOverEstimate=populationSizeOverEstimate)
a <- validation$getValidatedCredibilityIntervalsProportions(scenarios=paste0(scenarios, "combined"), modelNames=modelNames)
b <- validation$getValidatedCredibilityIntervalsProportions(scenarios=paste0(scenarios, "combined"), modelNames=modelNames, probs=c(.25, .75), probsName="50%")
credibilityIntervals <- rbind(a, b)

p <- ggplot(credibilityIntervals, aes(scenario, Proportion, shape=Interval, colour=modelName)) + geom_point() +
  scale_shape_manual(values=c(16, 1)) + scale_colour_manual("Model", values=c("darkgray", "black"), labels=c("T", "ST")) +
  theme_minimal(base_size=10) + theme(panel.border=element_rect(fill="transparent")) +
  xlab("Scenario") + ylab("Proportion within CI")
print(p)
saveFigure(p, "manuscript-figure-5b.png", width=4, height=2)
```

```{r figure-5c}
study <- getStudy(scenario="A")
validation <- Validation(study=study, populationSizeOverEstimate=populationSizeOverEstimate)
a <- validation$getValidatedCredibilityIntervalsProportions(scenarios=paste0(scenarios, "10days"), modelNames=modelNames)
b <- validation$getValidatedCredibilityIntervalsProportions(scenarios=paste0(scenarios, "10days"), modelNames=modelNames, probs=c(.25, .75), probsName="50%")
credibilityIntervals <- rbind(a, b)

p <- ggplot(credibilityIntervals, aes(scenario, Proportion, shape=Interval, colour=modelName)) + geom_point() +
  scale_shape_manual(values=c(16, 1)) + scale_colour_manual("Model", values=c("darkgray", "black"), labels=c("T", "ST")) +
  theme_minimal(base_size=10) + theme(panel.border=element_rect(fill="transparent")) +
  xlab("Scenario") + ylab("Proportion within CI")
print(p)
saveFigure(p, "manuscript-figure-5c.png", width=4, height=2)
```

>>>>

plotCIProportions <- function(credibilityIntervals) {
  credibilityIntervals$CI <- credibilityIntervals$Interval
  p <- ggplot(credibilityIntervals, aes(scenario, Proportion, shape=CI, colour=modelName)) +
    geom_hline(aes(yintercept=.5), color="grey90") +
    geom_hline(aes(yintercept=.95), color="grey90") +
    geom_point() +
    scale_shape_manual(values=c(16, 1)) + scale_colour_manual("Model", values=c("darkgray", "black"), labels=c("T", "ST")) +
    theme_minimal(base_size=10) + theme(panel.border=element_rect(fill="transparent")) +
    xlab("Scenario") + ylab("Proportion within CI") +
    facet_wrap(~panel) + ylim(0, 1) +
    theme(panel.grid.major=element_blank(), panel.grid.minor=element_blank())
  return(p)
}
```

@@
